### 2022-11-14 NSF2022/Description/backgroundv3.tex
refs added

The PIs recently developed a new mathematical model of self-organization
in fluid systems~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM}. The
framework uses small, rigid bodies called ``granules'' to represent
parcels of suspended media. The granule shapes and boundary conditions
capture the local properties of the suspension, and instead of volume
fraction, a phase field function represents the properties of the
solvent. Our approach falls into the category of work that considers
particles as a discretization of a continuous problem; in this case one
is dealing with a particle method, as an alternative to other
discretization methods such as finite-difference, finite-element, and
spectral methods~\cite{Wilson2021ComparisonOT}. We have departed from
the terminology ``particles'', though, to emphasize the role played the
granules' finite size.

The framework is robust, flexible, and cuts across many of the
aforementioned challenges. (i) The granules are not fixed to a stencil,
affording flexibility in terms of morphology and topology---sufficiently
large forces will even pull groups of granules apart as physically
required. (ii) The model formulation is built around important details
like molecular orientations, and exhibits inter-molecular slip that must
be added into diffusive interface models post hoc. (iii) It is
straightforward to consider mixtures of granules with different shapes
and boundary conditions. Leveraging boundary integral and fast summation
methods, the dynamics can be solved in near-linear complexity in the
number of granules, which is equal to or better than the computational
complexity of related sharp interface methods.

@@

\subsection{Applications}
Since the framework is scale independent, it can be applied to a broad
range of nonspecific self-organization phenomena in surface chemistry,
biology, and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label (\S\ref{sec:specificaim1}, equation
\eqref{eq:amphiphilic_BC}) spontaneously self-organize to sequester the
hydrophobic fluid phase (Figure~\ref{fig:flow_map}). Changes in the
boundary conditions result in distinct morphologies
(Figure~\ref{fig:self-assembly2}) whose rheology can be further
investigated (\S\ref{sec:specificaim3}).
%
A concrete application the PIs have considered in their SIAM Multiscale
Modeling and Simulation and Journal of Fluid Mechanics
works~\cite{Fu2018_SIAM, FuQuRyYo22} is the problem of \emph{vesicle
hydrodynamics}. A vesicle is a small, fluid filled membrane sack. The
goal in vesicle hydrodynamics is to study flow patterns arising from the
interaction between membrane elasticity and the fluid.

\begin{wrapfigure}[10]{l}{0.48\textwidth}
\vspace{-5pt}
\includegraphics[width=0.48\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\vspace{-20pt}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}
%
A striking feature of our hydrodynamic simulations is their fidelity to
physics. The model contains a few parameters; granule radius $c$, decay
length $\epsilon$, surface tension $\gamma$. When these are set to
realistic values \cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian,
Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016}, we
quantitatively recover many of the well-known elastic moduli for
single-component lipid bilayers \cite{Nagle17, Nagle17-2,
LeVeWa14,NAGLE2000159}. Such agreement is a validation that
equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} correctly capture
the long-range interactions between amphiphilic granules (such as lipid
macromolecules) surfaces.
\begin{wrapfigure}[13]{l}{0.475\textwidth}
\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
  vesicle under large shear rates.}
\end{wrapfigure}

>>>>

The PIs recently developed a new mathematical model of self-organization
in fluid systems~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM}. The
framework uses small, rigid bodies called ``granules'' to represent
parcels of suspended media. The granule shapes and boundary conditions
capture the local properties of the suspension, and instead of volume
fraction, a phase field function represents the properties of the
solvent. Our approach falls into the category of work that considers
particles as a discretization of a continuous problem; in this case one
is dealing with a particle method, as an alternative to other
stencil-based discretization methods~\cite{Wilson2021ComparisonOT,Gross2020MeshfreeMO,
Sigurdsson2016HydrodynamicCO}.
We have departed from the terminology ``particles'', though,
to emphasize the role played elliptic equations and the granules'
finite size.

The framework is robust, flexible, and cuts across many of the
aforementioned challenges. (i) The granules are not fixed to a stencil,
affording flexibility in terms of morphology and topology---sufficiently
large forces will even pull groups of granules apart as physically
required. (ii) The model formulation is built around important details
like molecular orientations, and exhibits inter-molecular slip that must
be added into continuum models post hoc. (iii) It is
straightforward to consider mixtures of granules with different shapes
and boundary conditions. Leveraging boundary integral and fast summation
methods, the dynamics can be solved in near-linear complexity in the
number of granules, which is equal to or better than the computational
complexity of related sharp interface methods.

@@

\subsection{Applications}
Since the framework is scale independent, it can be applied to a broad
range of nonspecific self-organization phenomena in surface chemistry,
biology, and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label (\S\ref{sec:specificaim1}, equation
\eqref{eq:amphiphilic_BC}) spontaneously self-organize to sequester the
hydrophobic fluid phase (Figure~\ref{fig:flow_map}). Changes in the
boundary conditions result in distinct morphologies
(Figure~\ref{fig:self-assembly2}) whose rheology can be further
investigated (\S\ref{sec:specificaim3}).
%
A concrete application the PIs have considered in their SIAM Multiscale
Modeling and Simulation and Journal of Fluid Mechanics
works~\cite{Fu2018_SIAM, FuQuRyYo22} is the problem of \emph{vesicle
hydrodynamics}.
%A vesicle is a small, fluid filled membrane sack.
The
goal in vesicle hydrodynamics is to study flow patterns arising from the
interaction between membrane elasticity/viscoelasticity and the fluid
\cite{Gera2022SwingingAT,Cox2015TheEO,wangthesis,C6SM02452A,Strychalski2012ViscoelasticIB}.

\begin{wrapfigure}[10]{l}{0.5\textwidth}
\vspace{-5pt}
\includegraphics[width=0.5\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\vspace{-20pt}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}
%
A striking feature of our hydrodynamic simulations is their fidelity to
physics. The model contains a few parameters; granule radius $c$, decay
length $\epsilon$, surface tension $\gamma$. When these are set to
realistic values \cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian,
Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016}, we
quantitatively recover well-known elastic moduli for
single-component lipid bilayers \cite{Nagle17, Nagle17-2,
LeVeWa14,NAGLE2000159}. Such agreement is a validation that
equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} correctly capture
the long-range interactions between amphiphilic granules (such as lipid
macromolecules) surfaces.
\begin{wrapfigure}[13]{l}{0.475\textwidth}
\vspace{-0pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
  vesicle under large shear rates.}
\end{wrapfigure}

### 2022-11-14 NSF2022/Description/specificaim1v2.tex
refs added

The first step is to obtain some solid well-posedness results
for~\eqref{eq:RBT}--\eqref{eqn:stressbalance}. This system is an
autonomous ordinary differential equation for the body transformations
$\FF_i$ with the rate of change defined by a system of PDEs. Regarding
the PDE system, in the linear case and for fixed $t$, there is a unique
solution ($\phi, \uu$) under appropriate assumptions for the boundaries
and boundary data~\cite{manasthesis, rac-gre2016, LAX}. These define
instantaneous rigid body velocities and rotations, leading to the
following problem.
\begin{quotation}
  \noindent
  \textbf{Problem 1.} 
  Consider a collection of closed, disjoint granules $U_i$ with smooth
  boundary, with no-slip, rigid body motion boundary conditions, and a
  linear background flow. Assume a single-well potential and a smooth
  phase field boundary conditions. What is the well-posedness in time of
  the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}?
\end{quotation}
Problem 1 involves mathematically interesting techniques. First, we must
establish that the system has a local-in-time solution. This involves
domain perturbations and estimates for the solutions of second order
elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
Lamboley2015EstimatesOF}, which also find extensive application in
extremal domain problems~\cite{Schiffer1954VariationOD,
Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
example. For global-in-time solutions, we can use lubrication
forces~\cite{cawthorn_balmforth_2010, leal_2007}. Here, the lubrication
force required to bring granules into contact blows up with distance,
and we must analyze whether the attraction~\eqref{eqn:stressbalance}
stays finite in order to guarantee positivity in the distance between
granules. Finally, we can study the granule-flow behavior in the
zero-decay length limit. This limit should recover the hydrodynamics of
a (noninteracting) rigid-body suspension.

\begin{wrapfigure}[11]{r}{0.5\textwidth}
  \vspace{-8pt}
  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:amphiphilic_assembly} \footnotesize
  Self-organization under amphiphilic boundary condition. (a) Granules
  first match hydrophobic tails (red), (b) then align length-wise. (c)
  The same pattern of self-organization holds in three dimensions, as
  simulated by Kohl, Corona, and
  Veerapaneni~\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
In the double-well potential case, equation~\eqref{eqn:phase} is a
nonlinear Allen-Cahn equation. This situation models granules immersed
in a two-phase fluid (e.g., granules in an emulsion) where there is an
interesting interplay between the long-range alignment of granules and
the diffusive interface energy of the free boundary between fluid
phases. On unbounded domains like $\Omega(t)$, Allen-Cahn equations can
have multiple solutions~\cite{Alama1997StationaryLS,
Alikakos2008OnAE, Bronsard1993OnTB, Byeon2014SolutionsOH, Byeon2013OnAP,
Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF} and so
we must reformulate~\eqref{eqn:phase}. An appropriate reformulation
is the following initial value problem with transport:
\begin{align}
  \label{eqn:phase_transport}
  \phi_t + \uu \cdot \nabla
  = -\beta \frac{\delta E}{\delta \phi}
  = \beta(\epsilon^2 \Delta \phi - W'(\phi)),
  \quad \phi(\xx,0) = \phi_0(\xx),
\end{align}
for initial data $\phi_0$. The modified system enjoys an energy law
similar to~\eqref{eq:energy_law} with an addtional dissipation term
involving the square the Euler-Lagrange derivative $\frac{\delta
E}{\delta \phi}$ and dampening factor $\beta > 0$. There are several
works dealing with the characterization of the geometric evolution of
interfaces under the Allen-Cahn and Cahn-Hilliard
equations~\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF,
Dai2019WeakSF, Promislow2017ExistenceBA, Dai2015CompetitiveGE,
Promislow2012CriticalPO, Dai2022GeometricEO, Dai2020MinimizersFT,
Dai2013GeometricEO, Promislow2022UndulatedBI} and well-posedness
results when coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
Liu2012StrongSF, Giorgini2019WellPosednessOA, Wu2022WellposednessOA,
Gal2010AsymptoticBO, Giorgini2020DiffuseIM, Giorgini2019UniquenessAR}.
The proposed research extends these results to problems with moving
domains. A closely related and strongly developing direction in the area
of nematics liquid crystals concerns the interaction of Landau de Gennes
functionals with colloids, and studies the qualitative structure of
defects around single or multiple coloidal
particles~\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT,
Alama2021SaturnRD, PhysRevE.96.042702}. PI Ryham has several works on
membrane vesicles dealing both with Allen-Cahn formulations and
fluid-vesicle interactions~\cite{QiangDu09, RYHAM20112929, RyCoEi12,
Ryham2017OnTV}.

@@

Sharp interface models represent a membrane vesicle as an
inextensible, continuous, closed surface $\Sigma$ with elastic energy
\begin{align}
  \label{eq:Canham-Helfrich}
  \int_{\Sigma} k_B(H - k_0)^2\, dS,
\end{align}
where $H$ is the mean curvature, $k_0$ is a spontaneous curvature, and
$k_B$ is a bending modulus. One can also account for extensibility by
including in~\eqref{eq:Canham-Helfrich} an additional stretching term
$k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are
the deformed and equilibrium area densitities respectively.

@@

Finally, to consider three-dimensionsional effects, we will generalize
Problem 2 to \emph{numerically} study the energies of amphiphilic
granules confined to surfaces. Recent works on nematics on a surface have
studied the interplay between surface geometry and a director
field~\cite{Nestler2020PropertiesOS, Nitschke2018NematicLC,
Nestler2018OrientationalOO, Nitschke2019HydrodynamicII,
Nitschke2020LiquidCO}. Researchers have formulated finite element
methods~\cite{Bartels2012FiniteEM, Nochetto2015NumericsFL,
Nestler2019AFE} and studied minimizers~\cite{Segatti2014EquilibriumCO,
Segatti2014AnalysisOA}. In biophysics, researchers
have derived the generalized Helfrich energy for lipid bilayers that
involves coupling effects between lipid tilt to director
splay~\cite{Hamm2000ElasticEO, Terzi2019CurvatureTiltTO, Terzi2019ACQ,
  Terzi2017NovelTC, Pinigin2020NewCT}. It contains~\eqref{eq:Canham-Helfrich}
as a special case.
\begin{quotation}
  \noindent
  \textbf{Problem 3.} Simulate surfaces made up of three-dimensional,
  amphilic granules. Numerically investigate the limiting energy for
  large-$N_b$ suspensions.
\end{quotation}
We will study Problem 3 by simulating large granule-number membranes.
If, after thoroughly sampling shapes and boundary conditions,
it turns out that the granule energies are not described by
a nematic or  Helfrich-type energy, then we will change
hypotheses and look for alternative sharp interface elastic energies.
PI Ryham is well-qualified to lead this investigation.
In his much noticed Biophysical Journal and Nature
papers~\cite{RyKlYaCo16, Chetal16}, he calculated least energy
paths for \emph{membrane fusion} using a surface-director model based on
the general Helfrich energy. The energy barriers 
proved consistent with later results from molecular dynamic
simulation and experiment~\cite{SmRiMu19, 2017PNAS..114.1238F}.

>>>>

The first step is to obtain some solid well-posedness results
for~\eqref{eq:RBT}--\eqref{eqn:stressbalance}.
This system is an
autonomous ordinary differential equations (ODEs) for the body transformations
$\FF_i$ with the rate of change defined by a system of PDEs.
Strategies have been proposed for the solution of
coupled PDE/ODE systems 
\cite{Carichino2018EnergybasedOS,Quarteroni2016GeometricMM}.
Regarding \eqref{eq:RBT}--\eqref{eqn:stressbalance},
in the linear case and for fixed $t$, there is a unique
solution ($\phi, \uu$) under appropriate assumptions for the boundaries
and boundary data~\cite{manasthesis, rac-gre2016, LAX}. These define
instantaneous rigid body velocities and rotations, leading to the
following problem.
\begin{quotation}
  \noindent
  \textbf{Problem 1.} 
  Consider a collection of closed, disjoint granules $U_i$ with smooth
  boundary, with no-slip, rigid body motion boundary conditions, and a
  linear background flow. Assume a single-well potential and a smooth
  phase field boundary conditions. What is the well-posedness in time of
  the coupled system \eqref{eq:RBT}--\eqref{eqn:stressbalance}?
\end{quotation}
Problem 1 involves mathematically interesting techniques. First, we must
establish that the system has a local-in-time solution. This involves
domain perturbations and estimates for the solutions of second order
elliptic equations~\cite{Savar2002DomainPA, DANERS20081,
Lamboley2015EstimatesOF}, which also find extensive application in
extremal domain problems~\cite{Schiffer1954VariationOD,
Henrot2006ExtremumPF, bogosel:hal-03607776,Bogosel2022OnTP}, for
example.
For global-in-time solutions, we can use lubrication
forces~\cite{cawthorn_balmforth_2010, leal_2007}. Here, the lubrication
force required to bring granules into contact blows up with distance,
and we must analyze whether the attraction~\eqref{eqn:stressbalance}
stays finite in order to guarantee positivity in the distance between
granules.
Finally, we can study the granule-flow behavior in the
zero-decay length limit. This limit should recover the hydrodynamics of
a (noninteracting) rigid-body suspension.

\begin{wrapfigure}[11]{r}{0.5\textwidth}
  \vspace{-8pt}
  \centerline{\includegraphics[width=0.5\textwidth]{figures/SA1Figures/AmphiphilicAssembly.pdf}}
  \vspace{-8pt}
  \caption{\label{fig:amphiphilic_assembly} \footnotesize
  Self-organization under amphiphilic boundary condition. (a) Granules
  first match hydrophobic tails (red), (b) then align length-wise. (c)
  The same pattern of self-organization holds in three dimensions, as
  simulated by Kohl, Corona, and
  Veerapaneni~\cite{koh-cor-che-vee2021}.}
\end{wrapfigure}
In the double-well potential case, equation~\eqref{eqn:phase} is a
nonlinear Allen-Cahn equation. This situation models granules immersed
in a two-phase fluid (e.g., granules in an emulsion) where there is an
interesting interplay between the long-range alignment of granules and
the diffusive interface energy of the free boundary between fluid
phases. On unbounded domains like $\Omega(t)$, Allen-Cahn equations can
have multiple solutions~\cite{Alama1997StationaryLS,
Alikakos2008OnAE, Bronsard1993OnTB, Byeon2014SolutionsOH, Byeon2013OnAP,
Alessio2005ENTIRESI, Trumper2007ExistenceOA, Benci2019MultipleSF} and so
we must reformulate~\eqref{eqn:phase}. An appropriate reformulation
is the following initial value problem with transport:
\begin{align}
  \label{eqn:phase_transport}
  \phi_t + \uu \cdot \nabla
  = -\beta \frac{\delta E}{\delta \phi}
  = \beta(\epsilon^2 \Delta \phi - W'(\phi)),
  \quad \phi(\xx,0) = \phi_0(\xx),
\end{align}
for initial data $\phi_0$. The modified system enjoys an energy law
similar to~\eqref{eq:energy_law} with an addtional dissipation term
involving the square the Euler-Lagrange derivative $\frac{\delta
E}{\delta \phi}$ and dampening factor $\beta > 0$. There are several
works dealing with the characterization of the geometric evolution of
interfaces under the Allen-Cahn and Cahn-Hilliard
equations~\cite{Christlieb2019CompetitionAC, Gavish2011CurvatureDF,
Dai2019WeakSF, Promislow2017ExistenceBA, Dai2015CompetitiveGE,
Promislow2012CriticalPO, Dai2022GeometricEO, Dai2020MinimizersFT,
Dai2013GeometricEO, Promislow2022UndulatedBI, Gera2017CahnHilliardOS}
and well-posedness
results when coupled to flow in static domains~\cite{Jiang2017TwophaseIF,
Liu2012StrongSF, Giorgini2019WellPosednessOA, Wu2022WellposednessOA,
Gal2010AsymptoticBO, Giorgini2020DiffuseIM, Giorgini2019UniquenessAR}.
The proposed research extends these results to problems with moving
domains. A closely related and strongly developing direction in the area
of nematics liquid crystals concerns the interaction of Landau de Gennes
functionals with colloids, and studies the qualitative structure of
defects around single or multiple coloidal
particles~\cite{doi:10.1098/rsta.2020.0432, Alama2015MinimizersOT,
  Alama2021SaturnRD, PhysRevE.96.042702}.

PI Ryham has several works on
membrane vesicles dealing both with Allen-Cahn formulations and
fluid-vesicle interactions~\cite{QiangDu09, RYHAM20112929, RyCoEi12,
Ryham2017OnTV}.

@@

Sharp interface models represent a membrane vesicle as an
inextensible, continuous, closed surface $\Sigma$ with elastic energy
\begin{align}
  \label{eq:Canham-Helfrich}
  \int_{\Sigma} k_B(H - k_0)^2\, dS,
\end{align}
where $H$ is the mean curvature, $k_0$ is a spontaneous curvature, and
$k_B$ is a bending modulus. One can also account
for spatially dependent spontaneous curvature
\cite{PhysRevE.79.031926,Lowengrub13,mahapatra_saintillan_rangamani_2020}
and for extensibility by
including in~\eqref{eq:Canham-Helfrich} an additional stretching term
$k_A(\alpha - \alpha_0)^2/\alpha_0^2$ where $\alpha$ and $\alpha_0$ are
the deformed and equilibrium area densitities respectively
\cite{chabanon2017}.

@@

Finally, to consider three-dimensionsional effects, we will generalize
Problem 2 to \emph{numerically} study the energies of amphiphilic
granules confined to surfaces. Recent works on nematics on a surface have
studied the interplay between surface geometry and a director
field~\cite{Nestler2020PropertiesOS, Nitschke2018NematicLC,
Nestler2018OrientationalOO, Nitschke2019HydrodynamicII,
Nitschke2020LiquidCO}. Researchers have formulated finite element
methods~\cite{Bartels2012FiniteEM, Nochetto2015NumericsFL,
Nestler2019AFE} and studied minimizers~\cite{Segatti2014EquilibriumCO,
Segatti2014AnalysisOA}. In biophysics, researchers
have derived the generalized Helfrich energy for lipid bilayers that
involves coupling effects between lipid tilt to director
splay~\cite{Hamm2000ElasticEO, Terzi2019CurvatureTiltTO, Terzi2019ACQ,
  Terzi2017NovelTC, Pinigin2020NewCT,Rangamani20140463}. It contains~\eqref{eq:Canham-Helfrich}
as a special case.
\begin{quotation}
  \noindent
  \textbf{Problem 3.} Simulate surfaces made up of three-dimensional,
  amphilic granules. Numerically investigate the limiting energy for
  large-$N_b$ suspensions.
\end{quotation}
We will study Problem 3 by simulating large granule-number membranes.
If, after thoroughly sampling shapes and boundary conditions,
it turns out that the granule energies are not described by
a nematic or  Helfrich-type energy, then we will change
hypotheses and look for alternative sharp interface elastic energies.
PI Ryham is well-qualified to lead this investigation.
In his much noticed Biophysical Journal and Nature
papers~\cite{RyKlYaCo16, Chetal16}, he calculated least energy
paths for \emph{membrane fusion} using a surface-director model based on
the general Helfrich energy. The energy barriers 
proved consistent with later results from molecular dynamic
simulation and experiment~\cite{SmRiMu19, 2017PNAS..114.1238F}.

### 2022-11-14 NSF2022/Description/specificaim2.tex
refs added

\begin{wrapfigure}[6]{l}{2.6in}
  \centering
%  \vspace{-10pt}
  \includegraphics[width=2.5in]{figures/SA2Figures/confinement.pdf}
  \vspace{-10pt}
  \caption{\label{fig:stenosis} \footnotesize A granule vesicle passing
  through a constricted geometry.}
\end{wrapfigure}

In experiments, it is known that interactions between bounding walls and
granules cannot be ignored~\cite{qua-gan-you2021,
KaouiHartingMisbah2011_PRE, her-sto-gra2005}. Therefore, the necessary
modification to the code will be implemented so that confinement can be
considered. This modification requires introducing an additional layer
potential on the bounding walls, and elements of this modification have
already been incorporated (Figure~\ref{fig:stenosis}). However, to
consider rheological properties of the suspensions, a periodic domain,
such as a Couette device, will be considered. Such multiply-connected
domains require additional modifications to the IE formulation. PI
Quaife is qualified to perform this task since he has simulated
suspensions with confinement for several projects including dynamic
suspensions~\cite{qua-bir2014, bys-sha-qua2020} and porous
media~\cite{chi-moo-qua2020, dea-qua-bir-jua2018, moo-che-chi-qua2022,
qua-gan-you2021}.
\begin{wrapfigure}[16]{r}{2.1in}
  \vspace{-4pt}
  \centering
  \input{figures/near_sing.tikz}
  \vspace{-15pt}
  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
  quadrature method that works in two and three dimensions. The
  spectrally-accurate trapezoid rule is used in points in
  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
  spacing.}
\end{wrapfigure}

The confinement introduces an additional computational
challenge---accurately computing integrals between nearly-touching
bodies. This issue is well-known in the IE community and several
algorithms have been developed in the last 30 years, including
panel-based methods~\cite{helsing_2008a, helsing_tutorial_2012},
Quadrature by Expansions (QBX)~\cite{din-hua-mar-tan2021,
klo-bar-gre-one2013, ste-bar2022, af2018sisc}, Barycentric-type formulae
for Cauchy integrals~\cite{bar2014, bar-wu-vee2015, ioa-pap-per1991},
and interpolation-based methods~\cite{ying_2006, qua-bir2014,
rah-vee-zor-bir2015} (Figure~\ref{fig:interpquad}). The proposed
research, which is described next, will combine several methods
including singularity subtraction, analytic function theory, and
analytic methods.

Since we are interested in round (2D) and spherical (3D) granules, we
will exploit the fact that integrals can be computed with spectral
accuracy by transforming the integrals to to a Fourier (2D) or spherical
harmonic (3D) basis. This technique can be used to evaluate layer
potentials for both Stokes~\cite{cor-vee2018} and the screened Laplace
equation~\cite{koh-cor-che-vee2021}. However, this quadrature is not
appropriate or other shapes, and an alternative approach is necessary.
The Barycentric-type formulae for Cauchy integrals results in a
uniformly bounded quadrature error, but the method is described only for
the two-dimensional Laplace and Stokes equations. PI Quaife recently
showed that these quadrature methods can be extended to other
two-dimensional PDEs~\cite{che-lin-her-qua2022}. The method uses
singularity subtraction to write the fundamental solution of the PDE as a
sum of two terms: a logarithmic function and a continuously
differentiable function. Then the Barycentric-type formulae can be
applied to the logarithmic function, and the standard trapezoid
rule~\cite{tre-wei2014} can be applied to the other function. These
singularity subtraction methods can also accurately compute derivatives
of layer potentials~\cite{car2021, car2020, car-kha-kim2018} which is
required, for example, when computing the phase
stress~\eqref{eqn:stressbalance}. Singularity subtraction methods can
also be applied in three dimensions, but not combined with
Barycentric-type formulae. Alternatively, smoothed variations of the
fundamental solution can be used to address nearly-singular
integrals~\cite{beale1, cor2001, tlu-bea2019}. Finally, efficient
quadrature methods can be applied directly to accurately compute
singular and near-singular integrals~\cite{khayat_2005,
gimbutas2013sisc}.

>>>>

In experiments, it is known that interactions between bounding walls and
granules cannot be ignored~\cite{qua-gan-you2021,
KaouiHartingMisbah2011_PRE, her-sto-gra2005}. Therefore, the necessary
modification to the code will be implemented so that confinement can be
considered. This modification requires introducing an additional layer
potential on the bounding walls, and elements of this modification have
already been incorporated (Figure~\ref{fig:stenosis}). However, to
consider rheological properties of the suspensions, a periodic domain,
such as a Couette device, will be considered. Such multiply-connected
domains require additional modifications to the IE formulation. PI
Quaife is qualified to perform this task since he has simulated
suspensions with confinement for several projects including dynamic
suspensions~\cite{qua-bir2014, bys-sha-qua2020} and porous
media~\cite{chi-moo-qua2020, dea-qua-bir-jua2018, moo-che-chi-qua2022,
qua-gan-you2021}.

\begin{wrapfigure}[6]{l}{2.6in}
  \centering
%  \vspace{-10pt}
  \includegraphics[width=2.5in]{figures/SA2Figures/confinement.pdf}
  \vspace{-10pt}
  \caption{\label{fig:stenosis} \footnotesize A granule vesicle passing
  through a constricted geometry.}
\end{wrapfigure}
The confinement introduces an additional computational
challenge---accurately computing integrals between nearly-touching
bodies. This issue is well-known in the IE community and several
algorithms have been developed in the last 30 years, including
panel-based methods~\cite{helsing_2008a, helsing_tutorial_2012},
Quadrature by Expansions (QBX)~\cite{din-hua-mar-tan2021,
klo-bar-gre-one2013, ste-bar2022, af2018sisc}, Barycentric-type formulae
for Cauchy integrals~\cite{bar2014, bar-wu-vee2015, ioa-pap-per1991},
and interpolation-based methods~\cite{ying_2006, qua-bir2014,
rah-vee-zor-bir2015} (Figure~\ref{fig:interpquad}). The proposed
research, which is described next, will combine several methods
including singularity subtraction, analytic function theory, and
analytic methods.

\begin{wrapfigure}[16]{r}{2.1in}
  \vspace{-4pt}
  \centering
  \input{figures/near_sing.tikz}
  \vspace{-15pt}
  \caption{\label{fig:interpquad} \footnotesize An interpolation-based
  quadrature method that works in two and three dimensions. The
  spectrally-accurate trapezoid rule is used in points in
  $\mathtt{Far}(\Gamma_i)$, while one dimensional interpolant is used
  for points in $\mathtt{Near}(\Gamma_i)$. $h$ is the arclength
  spacing.}
\end{wrapfigure}
Since we are interested in round (2D) and spherical (3D) granules, we
will exploit the fact that integrals can be computed with spectral
accuracy by transforming the integrals to to a Fourier (2D) or spherical
harmonic (3D) basis. This technique can be used to evaluate layer
potentials for both Stokes~\cite{cor-vee2018} and the screened Laplace
equation~\cite{koh-cor-che-vee2021}. However, this quadrature is not
appropriate or other shapes, and an alternative approach is necessary.
The Barycentric-type formulae for Cauchy integrals results in a
uniformly bounded quadrature error, but the method is described only for
the two-dimensional Laplace and Stokes equations. PI Quaife recently
showed that these quadrature methods can be extended to other
two-dimensional PDEs~\cite{che-lin-her-qua2022}. The method uses
singularity subtraction to write the fundamental solution of the PDE as a
sum of two terms: a logarithmic function and a continuously
differentiable function. Then the Barycentric-type formulae can be
applied to the logarithmic function, and the standard trapezoid
rule~\cite{tre-wei2014} can be applied to the other function. These
singularity subtraction methods can also accurately compute derivatives
of layer potentials~\cite{car2021, car2020, car-kha-kim2018} which is
required, for example, when computing the phase
stress~\eqref{eqn:stressbalance}. Singularity subtraction methods can
also be applied in three dimensions, but not combined with
Barycentric-type formulae. Alternatively, smoothed variations of the
fundamental solution can be used to address nearly-singular
integrals~\cite{beale1, cor2001, tlu-bea2019}. Finally, efficient
quadrature methods can be applied directly to accurately compute
singular and near-singular integrals~\cite{khayat_2005,
gimbutas2013sisc}.
